\bf Supplementary Material to\\ ``Nonparametric Block Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test''

### 2025-10-20 manuscript/manuscript.tex
minor
smoothed supplement

In theory, both $K_n(x)$ and $C_n(x)$ serve the same purpose of
centering the bootstrap goodness-of-fit process, and the circular
block bootstrap reproduces the temporal dependence structure of the
data. The two corrections aims the same centering, differing only in
whether the centering uses bootstrap expectations or sample-based
estimates. Additional simulations (see Section~1 of the Supplement)
show that, across all dependence levels and sample sizes considered,
the empirical sizes and powers were nearly identical. For the settings
studied, the two corrections performed nearly identically; we retain
$K_n(x)$ for conceptual clarity and consistency of presentation.

@@

We generated time series with marginal distributions $N(8, 8)$ and
$\Gamma(8, 1)$ with seven levels of Kendall's
$\tau \in \{-.75, -.50, -.25, 0, .25, .50, .75\}$, and
sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as a
measure of serial dependence between $X_i$ and
$X_{i+1}$ as it is invariant to monotone marginal
transformations.
To generate the samples to which our
method would be applied, we simulated a time series $W_i$ from a 1st
order autoregressive or AR(1) process:
\begin{equation*}
W_i = \phi W_{i-1} + \epsilon_i,
\end{equation*}
where $\phi$ is an autoregressive coefficient, and $\epsilon_i$ is a series of
independent errors from a normal distribution with mean zero and variance
$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
$\phi$, which was set to seven levels:
$\{-0.924, -0.707, -0.383, 0, 0.383, 0.707, 0.924\}$, as these
correspond to the desired values for $\tau$. The
series $W_i$ has mean zero and variance
$\sigma_x^2 = \sigma_{\epsilon}^2 / (1 - \phi^2)$, so for each value of
$\phi$,  we
set $\sigma_{\epsilon}^2 = (1 - \phi^2)$ such that $\sigma_x^2 = 1$.
First, we generated a
marginal $N(8, 8)$ by marginally transforming $W_i$ by
\begin{equation*}
X_i = F^{-1}[\Phi(W_i)],
\end{equation*}
where $F^{-1}(p)$ is the quantile function for the $N(8, 8)$
distribution and $\Phi$ is the distribution function of the standard normal
distribution.
Then we generated a marginal gamma series by the same procedure, but
replacing $F^{-1}(p)$ with the quantile function for the $\Gamma(8, 1)$
distribution. After the transformation
to the marginal gamma distribution, the lag-1 autocorrelations are approximately
\[
  \{-0.876, -0.674, -0.368, 0, 0.377, 0.701, 0.922\}.
\]

These distributions
were chosen to compare results on normal and non-normal
error structures. The specific parameters were chosen because the distributions
are very similar and their first two moments are the same. For the purposes of
evaluating if the test holds it size, when $X_i \sim N(8, 8)$, we tested that the
marginal distribution is from the
Normal family, or
$X_i \sim N(\cdot ; \mu, \sigma^2), \quad i = 1, \ldots, n$
for some unspecified $\mu$ and $\sigma$. When $X_i \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is from the Gamma family,
or
$X_i \sim \Gamma(\cdot ; \alpha, \beta), \quad i = 1, \ldots, n$.
for some unspecified $\alpha$ and $\beta$. For the block bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
As noted in Subsection~\ref{sub:npbb}, previous literature
suggests varying block size based on the dependence structure of the series.

For this reason, we also tried implementing our algorithm using the
plug-in approach for circular bootstrap block size introduced in
\citet{politis2004automatic}. Results and a discussion of this
additional simulation study are provided in Section~2
in the Supplement. We also compared empirical performance for the
block bootstrap KS test when using the $K_n(x)$ correction
versus the $C_n(x)$. The $K_n(x)$ correction was used
in the main manuscript whereas results and a discussion for the
$C_n(x)$ correction is included in the supplement.
For each setting for $F$, $\tau$, and $n$, we replicate the method
10000 times to get the distribution of the p-values $p_r$ for
$r \in \{1, \dots, 10000\}$
for the test when applied to samples from the same data generating
process.

\begin{figure}[tbp]
  \includegraphics[width = .9\textwidth]{figures/normal}
  \centering
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal normal distribution with true data generating distribution
    being $N(8,8)$.}
  \label{fig:qq_n}
    \hspace{5cm}
  \includegraphics[width = .9\textwidth]{figures/gamma}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal gamma distribution with true data
    generating distribution $\Gamma(8,1)$.}
  \label{fig:qq_g}
\end{figure}

@@

The plots suggest that the extent to which the p-values are uniformly
distributed is dependent on the sample size and the level of serial dependence.
A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
$\tau$ has an absolute value $|\tau| \leq 0.25$. For $|\tau| \geq 0.5$, 
a sample larger than
$n = 200$ seems necessary for the p-values to be uniformly distributed. For
$|\tau| \geq 0.75$, a sample larger than $n = 800$ appears to be
necessary, as the p-values are not aligned with the line in any of the Q-Q
plots. This is not necessarily a cause for concern, as (for normal margins)
a Kendall's $\tau$ of 0.75 corresponds to a $\phi$ of 0.924, which is very high.
Additionally, positive serial dependence appears to misalign the distribution
of the p-values more so than negative serial dependences of the same strength.
Results are very similar for normal and gamma margins.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/rr}
  \caption{Empirical power curve as a function of $\tau$ for
    $n \in \{100, 200, 400, 800\}$ and true marginal distribution
    $\in \{N(8,8), \Gamma(8,1)\}$. When the data was generated from $N(8,8)$,
    we tested for the gamma family. When the data was generated from
    $\Gamma(8,1)$, we tested for the normal family.
  }
  \label{fig:rr}
\end{figure}

Figure~\ref{fig:rr} displays the empirical power curve of the test at
significance level 0.05 as the lag-1 Kendall's~$\tau$ increases from
$-0.5$ to $0.5$. We omitted $-0.75$ and 0.75 from this study because we already
found that our method doesn't work under the null hypothesis for such high
dependence levels under the sample sizes considered. It appears that the
rejection rate seems to decline as $\tau$
increases. Rejection rates are negatively affected by positive serial
dependence, but they do not seem to be affected by negative serial dependencies
of the same strength.
Using $n \geq 400$ seems to be good enough
if $\tau < 0.5$, but using a $n \geq 800$ will result in
rejection rates close to 1 for $-0.5 < \tau < 0.5$. 
Results for $n \geq 400$
do not appear to be to different when comparing gamma and normal
margins, indicating that the method is robust to the marginal distribution.
The rejection rates for $n = 800$ are very
high (almost 1), indicating that under $H_A$, the test is very powerful
when a large enough sample size is used.

@@

While differences in p-values among different methods are expected, our analysis
reveals some instances where conclusions at the 0.05 significance level
using our method differ from those obtained using the methods proposed by
\citet{babu2004goodness} and \citet{zeimbekakis2024misuses}.
For example, our NPBB method fails to reject the
hypothesis that the series follows a Student's $t$ distribution with degrees of
freedom $\nu = 5$ with a p-value of 0.061. In contrast,
the SPB method yields a p-value of 0.0192,
the NPB method yields a p-value of 0.0222, and the PB yields a p-value of
0.0141. Although such differences are not guaranteed, this
instance highlights a disagreement in conclusions among methods for the S\&P 500
index. Because NPB and PB both discard serial dependence, it is expected that
their conclusions could be different from our method. It is worth noting that
the SPB result is also not reliable here because the working dependence model is
in the class of ARMA dependence as specified in \citet{zeimbekakis2024misuses},
which does not cover nonlinear dependence usually captured by autoregressive
conditional heteroskedasticity \citep{engle1995arch}. The proposed method has
no need to specify the serial dependence and, hence, produces results under
weakest assumptions.

>>>>

In theory, both $K_n(x)$ and $C_n(x)$ serve the same purpose of
centering the bootstrap goodness-of-fit process, and the circular
block bootstrap reproduces the temporal dependence structure of the
data. The two corrections aims the same centering, differing only in
whether the centering uses bootstrap expectations or sample-based
estimates. Additional simulations (see Section~S-1 of the Supplement)
show that, across all dependence levels and sample sizes considered,
the empirical sizes and powers were nearly identical. For the settings
studied, the two corrections performed nearly identically; we retain
$K_n(x)$ for conceptual clarity and consistency of presentation.

@@

We generated time series with marginal distributions $N(8, 8)$ and
$\Gamma(8, 1)$ with seven levels of Kendall's
$\tau \in \{-.75, -.50, -.25, 0, .25, .50, .75\}$, and
sample size $n \in \{100, 200, 400, 800\}$. Kendall's $\tau$ was chosen as a
measure of serial dependence between $X_i$ and
$X_{i+1}$ as it is invariant to monotone marginal
transformations.
To generate the samples to which our
method would be applied, we simulated a time series $W_i$ from a 1st
order autoregressive or AR(1) process:
\begin{equation*}
W_i = \phi W_{i-1} + \epsilon_i,
\end{equation*}
where $\phi$ is an autoregressive coefficient, and $\epsilon_i$ is a series of
independent errors from a Normal distribution with mean zero and variance
$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
$\phi$, which was set to seven levels:
$\{-0.924, -0.707, -0.383, 0, 0.383, 0.707, 0.924\}$, as these
correspond to the desired values for $\tau$. The
series $W_i$ has mean zero and variance
$\sigma_x^2 = \sigma_{\epsilon}^2 / (1 - \phi^2)$, so for each value of
$\phi$,  we
set $\sigma_{\epsilon}^2 = (1 - \phi^2)$ such that $\sigma_x^2 = 1$.
First, we generated a
marginal $N(8, 8)$ by marginally transforming $W_i$ by
\begin{equation*}
X_i = F^{-1}[\Phi(W_i)],
\end{equation*}
where $F^{-1}(p)$ is the quantile function for the $N(8, 8)$
distribution and $\Phi$ is the distribution function of the standard Normal
distribution.
Then we generated a marginal Gamma series by the same procedure, but
replacing $F^{-1}(p)$ with the quantile function for the $\Gamma(8, 1)$
distribution. After the transformation
to the marginal Gamma distribution, the lag-1 autocorrelations are approximately
\[
  \{-0.876, -0.674, -0.368, 0, 0.377, 0.701, 0.922\}.
\]

These distributions
were chosen to compare results on Normal and non-Normal
error structures. The specific parameters were chosen because the distributions
are very similar and their first two moments are the same. For the purposes of
evaluating if the test holds it size, when $X_i \sim N(8, 8)$, we tested that the
marginal distribution is from the
Normal family, or
$X_i \sim N(\cdot ; \mu, \sigma^2), \quad i = 1, \ldots, n$
for some unspecified $\mu$ and $\sigma$. When $X_i \sim \Gamma(8, 1)$, we tested
that the marginal distribution family is from the Gamma family,
or
$X_i \sim \Gamma(\cdot ; \alpha, \beta), \quad i = 1, \ldots, n$.
for some unspecified $\alpha$ and $\beta$. For the block bootstrap step,
we used $B = 1000$ and $l = \lceil n^{1/3} \rceil$.
As noted in Subsection~\ref{sub:npbb}, previous literature
suggests varying block size based on the dependence structure of the series.

For this reason, we also tried implementing our algorithm using the
plug-in approach for circular bootstrap block size introduced in
\citet{politis2004automatic}. Results and a discussion of this
additional simulation study are provided in Section~S-2
in the Supplement. We also compared empirical performance for the
block bootstrap KS test when using the $K_n(x)$ correction
versus the $C_n(x)$. The $K_n(x)$ correction was used
in the main manuscript whereas results and a discussion for the
$C_n(x)$ correction is included in the supplement.
For each setting for $F$, $\tau$, and $n$, we replicate the method
10000 times to get the distribution of the p-values $p_r$ for
$r \in \{1, \dots, 10000\}$
for the test when applied to samples from the same data generating
process.

\begin{figure}[tbp]
  \includegraphics[width = .9\textwidth]{figures/normal}
  \centering
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal Normal distribution with true data generating distribution
    being $N(8,8)$.}
  \label{fig:qq_n}
    \hspace{5cm}
  \includegraphics[width = .9\textwidth]{figures/gamma}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal Gamma distribution with true data
    generating distribution $\Gamma(8,1)$.}
  \label{fig:qq_g}
\end{figure}

@@

The plots suggest that the extent to which the p-values are uniformly
distributed is dependent on the sample size and the level of serial dependence.
A small sample size like $n = 100$ or $200$ seems adequate when Kendall's
$\tau$ has an absolute value $|\tau| \leq 0.25$. For $|\tau| \geq 0.5$, 
a sample larger than
$n = 200$ seems necessary for the p-values to be uniformly distributed. For
$|\tau| \geq 0.75$, a sample larger than $n = 800$ appears to be
necessary, as the p-values are not aligned with the line in any of the Q-Q
plots. This is not necessarily a cause for concern, as (for Normal margins)
a Kendall's $\tau$ of 0.75 corresponds to a $\phi$ of 0.924, which is very high.
Additionally, positive serial dependence appears to misalign the distribution
of the p-values more so than negative serial dependences of the same strength.
Results are very similar for Normal and Gamma margins.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/rr}
  \caption{Empirical power curve as a function of $\tau$ for
    $n \in \{100, 200, 400, 800\}$ and true marginal distribution
    $\in \{N(8,8), \Gamma(8,1)\}$. When the data was generated from $N(8,8)$,
    we tested for the Gamma family. When the data was generated from
    $\Gamma(8,1)$, we tested for the Normal family.
  }
  \label{fig:rr}
\end{figure}

Figure~\ref{fig:rr} displays the empirical power curve of the test at
significance level 0.05 as the lag-1 Kendall's~$\tau$ increases from
$-0.5$ to $0.5$. We omitted $-0.75$ and 0.75 from this study because we already
found that our method doesn't work under the null hypothesis for such high
dependence levels under the sample sizes considered. It appears that the
rejection rate seems to decline as $\tau$
increases. Rejection rates are negatively affected by positive serial
dependence, but they do not seem to be affected by negative serial dependencies
of the same strength.
Using $n \geq 400$ seems to be good enough
if $\tau < 0.5$, but using a $n \geq 800$ will result in
rejection rates close to 1 for $-0.5 < \tau < 0.5$. 
Results for $n \geq 400$
do not appear to be to different when comparing Gamma and Normal
margins, indicating that the method is robust to the marginal distribution.
The rejection rates for $n = 800$ are very
high (almost 1), indicating that under $H_A$, the test is very powerful
when a large enough sample size is used.

@@

While differences in p-values among different methods are expected, our analysis
reveals some instances where conclusions at the 0.05 significance level
using our method differ from those obtained using the methods proposed by
\citet{babu2004goodness} and \citet{zeimbekakis2024misuses}.
For example, our NPBB method fails to reject the
hypothesis that the series follows a Student's $t$ distribution with degrees of
freedom $\nu = 5$ with a p-value of 0.061. In contrast,
the SPB method yields a p-value of 0.0192,
the NPB method yields a p-value of 0.0222, and the PB yields a p-value of
0.0141. Although such differences are not guaranteed, this
instance highlights a disagreement in conclusions among methods for the S\&P 500
index. Because NPB and PB both discard serial dependence, it is expected that
their conclusions could be different from our method. It is worth noting that
the SPB result is also not reliable here because the working dependence model is
in the class of ARMA dependence as specified in \citet{zeimbekakis2024misuses},
which does not cover nonlinear dependence usually captured by autoregressive
conditional heteroskedasticity \citep{engle1995arch}. The NPBB method has
no need to specify the serial dependence and, hence, produces results under
weakest assumptions.

### 2025-10-20 manuscript/supplement.tex
smoothed supplement

%&latex
\documentclass[12pt]{article}
\usepackage{authblk}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL
\usepackage{comment}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{setspace}

@@

@@

A heuristic justification for the $K_n(x)$ bias correction term was
provided in the main manuscript. It may also help to demonstrate
empirically that this the block bootstrap KS test with the $K_n$ bias
correction holds its size at least as well as the block boostrap KS
test with the \citet{babu2004goodness} bias correction and is at
least as powerful. For this reason, we conducted a simulation study
with parameter settings identical to the main study in the paper
except for the choice of bias correction.

\begin{figure}[tbp]
  \includegraphics[width = .9\textwidth]{figures/normal_C_n}
  \centering
  \vspace{-10pt}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal normal distribution with true data generating distribution
    being $N(8,8)$ when using \citet{babu2004goodness}'s bias correction term.}
  \label{fig:qq_n_C_n}
    \hspace{3cm}
  \includegraphics[width = .9\textwidth]{figures/gamma_C_n}
  \vspace{-5pt}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal gamma distribution with true data generating distribution
    being $\Gamma(8,1)$ when using \citet{babu2004goodness}'s bias correction term.}
  \label{fig:qq_g_C_n}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/rr_C_n}
  \caption{Empirical power curve as a function of $\tau$ for
    $n \in \{100, 200, 400, 800\}$ and true marginal distribution
    $\in \{N(8,8), \Gamma(8,1)\}$, when using \citet{babu2004goodness}'s bias correction term. When the data was generated from $N(8,8)$,
    we tested for the gamma family. When the data was generated from
    $\Gamma(8,1)$, we tested for the normal family.
  }
  \label{fig:rr_C_n}
\end{figure}

Based on Figures~\ref{fig:qq_n_C_n, fig:qq_g_C_n, fig:rr_C_n}, the empirical performance is very similar under either choice of bias correction term. For practical applications, we recommend.....

@@

The choice of block size is a key factor influencing the performance
of block bootstrap methods, particularly in settings with serial
dependence. While our main simulations used a fixed block size
$l = \lceil n^{1/3} \rceil$, the optimal block size depends on the
stength and structure of dependence \citep{hall1995blocking,
  buhlmann1999block,  politis2004automatic}. Motivated by this, we
further examined the use of an automatic block-length selection scheme
as proposed by \citet{politis2004automatic}, which aims to adaptively
choose the block size based on the data. The simulation settings
remain the same as in the study reported earlier.

% To address this, we considered  using the automatic block-length selection
% scheme for circular block bootstrap as described in Section~3.3 of
% \citet{politis2004automatic}. Unfortunately, using this setting results in
% the selection of block
% sizes that can be quite large (sometimes as large or larger than $n$), leading
% to less variation between the bootstrapped
% samples. Figures~\ref{fig:large_block}
% demonstrate that for highly temporally
% dependent samples (especially when the autocorrelation is negative),
% the block size is frequently larger than $\sqrt{n}$. For more moderate 
% positive temporal dependence, the block size may not be overly large
% as frequently. Still, even for these moderately dependent samples, the 
% block sizes are almost always larger than $l = \lceil n^{1/3} \rceil$, a setting
% which was considered optimal by \citep{buhlmann1999block}. This
% is demonstrated in Figure~\ref{fig:block_dist} with a histogram
% of the selected block sizes for the 20000 samples with $n = 800$, $\tau = 0.5$, 
% and $X_i \sim N(8, 8)$.

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/block_dist}
  \caption{Distribution of the selected block sizes using
  \citet{politis2004automatic}'s procedure applied to 20000 length-800 time 
  series with
    Kendall's $\tau = 0.5$ data generating distribution $N(8,8)$. The vertical
    dashed line is $l = \lceil n^{1/3} \rceil$ for $n = 800$, which is equivalent 
    to 10.
  }
  \label{fig:block_dist}
% \end{figure}

@@

Automatic block size selection tends to yield larger block sizes than our
fixed choice $l = \lceil n^{1/3} \rceil$, as expected, but under strong
negative or very strong positive dependence it systematically produces
block sizes that are excessively large, sometimes as large as or larger
than $n$. Note that in our simulations, we set the final block size to 
$\min \{n, \hat l\}$, where
$\hat l$ is the block size selected by \citet{politis2004automatic}'s
procedure. Figure~\ref{fig:block_dist} illustrates the typical behavior by
showing the distribution of block sizes selected by \citet{politis2004automatic}
for $n = 800$, $\tau = 0.5$, and $X_i \sim N(8,8)$. The majority of selected
block sizes exceed $\lceil n^{1/3} \rceil$, and many approach or exceed
$\sqrt{n}$. Figure~\ref{fig:large_block} presents the proportion of selected
block sizes exceeding $\sqrt{n}$ across varying levels of dependence and sample 
sizes.
The selection of block sizes larger than $\sqrt{n}$ occurs systematically under 
strong
negative dependence, and is also frequent under very strong positive dependence.

\begin{figure}[tbp]
  \includegraphics[width = .9\textwidth]{figures/alt_normal}
  \centering
  \vspace{-10pt}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal normal distribution with true data generating distribution
    being $N(8,8)$, when using \citet{politis2004automatic}'s procedure
    to select block sizes.}
  \label{fig:alt_qq_n}
    \hspace{3cm}
  \includegraphics[width = .9\textwidth]{figures/alt_gamma}
  \vspace{-5pt}
  \caption{Q-Q plots of the p-values testing that a time series
    have marginal gamma distribution with true data generating distribution
    being $\Gamma(8,1)$, when using \citet{politis2004automatic}'s procedure
    to select block sizes.}
  \label{fig:alt_qq_g}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/alt_rr}
  \caption{Empirical power curve as a function of $\tau$ for
    $n \in \{100, 200, 400, 800\}$ and true marginal distribution
    $\in \{N(8,8), \Gamma(8,1)\}$, when using \citet{politis2004automatic}'s 
    procedure
    to select block sizes. When the data was generated from $N(8,8)$,
    we tested for the gamma family. When the data was generated from
    $\Gamma(8,1)$, we tested for the normal family.
  }
  \label{fig:alt_rr}
\end{figure}

We evaluated the size and power performance of the NPBB test under automatic
block length selection. The size performance is shown
in Figures~\ref{fig:alt_qq_n} and \ref{fig:alt_qq_g}, which display Q-Q plots
of the $p$-values under the null for Normal and Gamma margins, respectively.
Recall from Figures~\ref{fig:qq_n} and \ref{fig:qq_g} that the cubic root 
setting holds its size quite well with small $n$ for $|\tau| \leq 0.25$,
whereas achieving nominal size for $|\tau| \geq 0.5$ require
$n > 200$, and for $|\tau| \geq 0.75$ require $n > 800$. The automatic
selection shows similar limitations for $|\tau| > 0.5$, where it does
not hold its size. Moreover, deviations from the diagonal line appear
larger for negative $\tau$, likely due to the high proportion of
occurrence of overly large block sizes. For example, while the cubic
root setting held its size well at $\tau = -0.25$ with small~$n$, the
automatic selection does not. At the same time, under $\tau = 0$ or
$\tau = 0.25$, the method with block size selected by
\citep{politis2004automatic} maintains reasonable size for moderately
positively dependent series.

Figure~\ref{fig:alt_rr} shows the power results under automatic selection.
When compared to Figure~\ref{fig:rr}, the two settings exhibit similar power
for $|\tau| \leq 0.5$, with the automatic selection sometimes yielding higher
rejection rates, particularly for smaller negatively dependent samples.
Overall, while the automatic selection from \citep{politis2004automatic}
performs reasonably well in certain settings, we recommend caution when using
it under negative~$\tau$ and smaller sample sizes, where maintaining nominal
size may be more difficult. In such cases, it may be sensible to apply a more
restrictive rule when setting the final block size---for example, using
$\min \{\sqrt{n}, \hat{l}\}$.

>>>>

\documentclass[12pt]{article}
\usepackage{authblk}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{url} % not crucial - just used below for the URL
\usepackage{comment}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{setspace}

@@

\renewcommand{\thefigure}{S-\arabic{figure}}
\renewcommand{\thetable}{S-\arabic{table}}
\renewcommand{\thesection}{S-\arabic{section}}

@@

\begin{figure}[tbp]
  \includegraphics[width = .9\textwidth]{figures/normal_C_n}
  \centering
  \vspace{-10pt}
  \caption{Q-Q plots of the p-values testing that a time series
    has a marginal Normal distribution with true data generating distribution
    being $N(8,8)$ when using  bias correction term $C_n$.}
  \label{fig:qq_n_C_n}
    \hspace{3cm}
  \includegraphics[width = .9\textwidth]{figures/gamma_C_n}
  \vspace{-5pt}
  \caption{Q-Q plots of the p-values testing that a time series
    has a marginal Gamma distribution with true data generating distribution
    being $\Gamma(8,1)$ when using  bias correction term $C_n$.}
  \label{fig:qq_g_C_n}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/rr_C_n}
  \caption{Empirical power curve as a function of $\tau$ for
    $n \in \{100, 200, 400, 800\}$ and true marginal distribution
    $\in \{N(8,8), \Gamma(8,1)\}$, when using bias correction term
    $C_n$. When the data was generated from $N(8,8)$,
    we tested for the Gamma family. When the data was generated from
    $\Gamma(8,1)$, we tested for the Normal family.
  }
  \label{fig:rr_C_n}
\end{figure}

To evaluate the practical difference between the two bias correction
terms, this section presents a direct comparison between the
nonparametric block bootstrap KS tests based on $K_n(x)$ and on
$C_n(x)$. The $K_n(x)$ correction, which was heuristically justified in
the main manuscript, is designed to center the empirical process in a
manner consistent with the dependence structure of the series. In
contrast, $C_n(x)$ is the bias correction proposed by
\citet{babu2004goodness} for independent observations.

A simulation study was conducted using the same settings as in the main
paper, varying sample size, block length, and dependence strength, with
the only difference being the choice of bias correction term.
Figures~\ref{fig:qq_n_C_n}--\ref{fig:rr_C_n} present the results for
$C_n(x)$, which are the counterparts of the figures in the main
manuscript obtained
using $K_n(x)$. Across the same parameter configurations, both versions
of the test maintain comparable size and power, and their performance
differences appear negligible for the cases examined.

These findings suggest that, within the range of settings studied, the
circular block bootstrap already removes most dependence-induced bias,
so that the additional centering adjustment has limited practical
impact. Although $C_n(x)$ requires slightly less computation, we
continue to recommend $K_n(x)$ for its theoretical motivation, while
recognizing that in the present experiments their empirical behavior is
essentially indistinguishable.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/block_dist}
  \caption{Distribution of the selected block sizes using
    \citet{politis2004automatic}'s procedure applied to 20,000
    time series of length-800 with
    Kendall's $\tau = 0.5$ data generating distribution $N(8,8)$. The vertical
    dashed line marks $l = \lceil n^{1/3} \rceil \approx 10$.
  }
  \label{fig:block_dist}
% \end{figure}

@@

The choice of block size plays a central role in determining the
finite-sample behavior of block bootstrap methods when serial
dependence is present. Although our main simulations used the fixed rule
$l = \lceil n^{1/3} \rceil$, the effective block size can vary with the
strength and pattern of dependence
\citep{hall1995blocking, buhlmann1999block, politis2004automatic}.
To evaluate the impact of data-driven selection, we examined the
automatic block-length procedure proposed by
\citet{politis2004automatic}, which selects the block size adaptively
from the observed series. All other simulation settings were kept
identical to those in the main paper.

The automatically selected block sizes were generally larger than the
fixed choice $l = \lceil n^{1/3} \rceil$, as anticipated, but the
procedure sometimes produced unrealistically large values under certain
dependence structures. In particular, when the series exhibited strong
negative or very strong positive dependence, the selected block sizes
were often excessively large---occasionally comparable to or exceeding
the sample size $n$. In our implementation, we set the final block
length to $\min\{n, \hat{l}\}$, where $\hat{l}$ denotes the value
returned by the automatic procedure. Figure~\ref{fig:block_dist}
illustrates the typical distribution of selected block sizes for $n =
800$, $\tau = 0.5$, and $X_i \sim N(8,8)$, showing that most values
exceed $\lceil n^{1/3} \rceil$ and many approach or surpass
$\sqrt{n}$. Figure~\ref{fig:large_block} further summarizes the
proportion of selected block sizes greater than $\sqrt{n}$ across
different dependence levels and sample sizes, indicating that such
oversizing occurs systematically under strong negative and very strong
positive dependence.

\begin{figure}[tbp]
  \includegraphics[width = .9\textwidth]{figures/alt_normal}
  \centering
  \vspace{-10pt}
  \caption{Q-Q plots of the p-values testing that a time series
    has a marginal Normal distribution with true data generating distribution
    being $N(8,8)$, when using \citet{politis2004automatic}'s procedure
    to select block sizes.}
  \label{fig:alt_qq_n}
    \hspace{3cm}
  \includegraphics[width = .9\textwidth]{figures/alt_gamma}
  \vspace{-5pt}
  \caption{Q-Q plots of the p-values testing that a time series
    has a marginal Gamma distribution with true data generating distribution
    being $\Gamma(8,1)$, when using \citet{politis2004automatic}'s procedure
    to select block sizes.}
  \label{fig:alt_qq_g}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[scale=1]{figures/alt_rr}
  \caption{Empirical power curve as a function of $\tau$ for
    $n \in \{100, 200, 400, 800\}$ and true marginal distribution
    $\in \{N(8,8), \Gamma(8,1)\}$, when using \citet{politis2004automatic}'s 
    procedure
    to select block sizes. When the data was generated from $N(8,8)$,
    we tested for the Gamma family. When the data was generated from
    $\Gamma(8,1)$, we tested for the Normal family.
  }
  \label{fig:alt_rr}
\end{figure}

We next evaluated the size and power performance of the NPBB test when
the block length was chosen automatically.
Figures~\ref{fig:alt_qq_n} and~\ref{fig:alt_qq_g} display the empirical
size through Q--Q plots of the $p$-values under the null for Normal and
Gamma margins, respectively. For reference, the main paper showed that
the fixed cubic root rule $l = \lceil n^{1/3} \rceil$ maintained size
reasonably well for small~$n$ when $|\tau| \le 0.25$, whereas achieving
nominal size required $n > 200$ for $|\tau| \ge 0.5$ and $n > 800$ for
$|\tau| \ge 0.75$. The automatic selection exhibits a similar pattern
of limitations: for $|\tau| > 0.5$, the empirical size again departs
from nominal levels. Deviations from the diagonal line are more
pronounced for negative~$\tau$, consistent with the high frequency of
excessively large block sizes in those cases. For instance, while the
cubic root rule held size adequately at $\tau = -0.25$ with small~$n$,
the automatic procedure no longer does. In contrast, for
$\tau \in \{0, 0.25\}$, the automatically selected block sizes yield
size control comparable to the fixed rule, indicating satisfactory
performance for weak or moderate positive dependence.

Figure~\ref{fig:alt_rr} summarizes the power analysis under automatic
selection. Relative to the main paper’s results based on the cubic root
rule, the two approaches show broadly similar power for
$|\tau| \le 0.5$, with the automatic method occasionally achieving
slightly higher rejection rates for small samples with mild negative
dependence. Overall, these findings indicate that the automatic
procedure of \citet{politis2004automatic} performs reasonably well under
most conditions studied but may yield unstable results when dependence
is negative and sample sizes are small. In such cases, it is advisable
to adopt a more restrictive cap on the final block size---for example,
setting it to $\min\{\sqrt{n}, \hat{l}\}$---to avoid excessive block
lengths that can distort the bootstrap resampling.
